% HEADER and settings -- do not change
\documentclass[final,a4paper]{aust_thesis}
\usepackage{definitions}
%%


% The set of languages we want to show
\lstloadlanguages{Python}

% one can select one...
\lstset{language=Python}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%!!          THIS WILL BE CHANGED       !!%%%%

%%   FRONT MATTER  
\submityear{%
2019%
}
\submitmonth{%
July%
}
\title{%
Sentiment Analysis Based on Social Media Data
}
\author{%
Kudzai Zishumba
}
\tutor{%
Prof. dr. Lehel Csat\'o\\
~\\
Faculty of Mathematics and Informatics,\hspace*{-3cm}\\
Babe\c{s} Bolyai University of Cluj-Napoca,\hspace*{-3cm}\\
Romania
}

% this is to speed up compilation...

%\includeonly{intro}


\begin{document}

%% ABSTRACT
\begin{abstract}%

Sentiment analysis is a challenging natural language processing (NLP) problem.
%
Our task here us to build an artificial agent -- or an AI system -- that is capable of detecting polarity in a document.
%
But more information such as the emotion of the author can be obtained.
%
In a general sense, sentiment analysis determines the opinion regarding the object/subject in discussion.
%
But emotion detection can identify the particular ``mood'' of the author.
%
Social platforms -- such as Facebook, Twitter, IMDB, or comment sections from newspapers -- to name a few -- can provide a huge corpus of -- usually unlabelled or extremely sparsely labelled -- content.

Using modern machine learning tools and the available computational power, an agent can analyse the content -- given usually as a list of messages -- and detect the general emotion ``within the message''.
%
It is capable of identifying subjects with unstable or ``chaotic'' mood that might require attention.

Our aim is to attempt detecting the underlying emotion as well as the polarity of a document.
%
In this process we will make use of open source libraries and publicly available data sets.
%
The program will be able to run locally, both in geographic and in cultural sense, and to analyse the results that were obtained.

~

This work is the result of my own activity. I have neither given nor received unauthorized assistance on this work.

\end{abstract}

% this command generates the titlepage
\maketitle

%% 

% this command generates the table of contents
{ \baselineskip 1ex
  \parskip 1ex
  \tableofcontents
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%    the structure of your thesis     %%%%%%%%%%%%


% the document is structured into LOGICAL parts:
\include{intro.tex}

\include{theory}

\include{analysis}

\include{experim}

\appendix
\include{programs}


{ \renewcommand{\baselinestretch}{0.8}\normalsize %
  \setlength{\itemsep}{-2.4mm}
  \setlength{\bibspacing}{0.67\baselineskip}
  \bibliographystyle{abbrvnat}
  \bibliography{thesis}
}

\end{document}
